% TODO: sistemare bibliografia con latex.
% Questi appartengono sia a cryptonight che cryptonight 

\section{Problemi di CryptoNight}\label{problemi-di-cryptonight}

{[}1\^{}{]} Tatsuaki Okamoto, Kazuo Ohta, ``Universal Electronic Cash,''
Advances in Cryp-tology \textbar{} CRYPTO '91, LNCS 576, pp.~324-337,
1991.

{[}2\^{}{]} Hart, P. E.; Nilsson, N. J.; Raphael, B. (1968). ``A Formal
Basis for the Heuristic Determination of Minimum Cost Paths''. IEEE
Transactions on Systems Science and Cybernetics SSC4 4 (2): 100-107.

{[}3\^{}{]} Fergal Reid, Martin Harrigan, \An Analysis of Anonymity in
the Bitcoin System'',2012.

{[}4\^{}{]} Kay Hamacher, Stefan Katzenbeisser, \Bitcoin - An
Analysis'', 2011, http://www.youtube.com/watch?v=hlWyTqL1hFA

{[}5\^{}{]} Dorit Ron, Adi Shamir, \Quantitative Analysis of the Full
Bitcoin Transaction Graph'', 2012.

{[}6\^{}{]} https://en.bitcoin.it/wiki/Category:Mixing\_Services

{[}7\^{}{]}
http://blog.ezyang.com/2012/07/secure-multiparty-bitcoin-anonymization

{[}8\^{}{]} https://en.bitcoin.it/wiki/BIP\_0034\#Specification

{[}9\^{}{]} https://en.bitcoin.it/wiki/Mining\_hardware\_comparison

{[}10\^{}{]} https://en.bitcoin.it/wiki/Contracts

{[}11\^{}{]} https://en.bitcoin.it/wiki/Script

{[}12\^{}{]} D. Chaum and E. van Heyst (1991). ``Group signatures''.
Advances in Cryptology\textbar{} EUROCRYPT '91, volume 547 of Lecture
Notes in Computer Science. pp.~257-265.

{[}13\^{}{]} Ronald L. Rivest , Adi Shamir , Yael Tauman, How to Leak a
Secret, Proceedings of the 7th International Conference on the Theory
and Application of Cryptology and Information Security: Advances in
Cryptology, p.552-565, December 09-13, 2001

{[}14\^{}{]} Fujisaki, E., Suzuki, K.: Traceable ring signature. IEICE
Trans. of Fund. E91-A(1), 83-93 (2008); Presented in PKC 2007, LNCS 4450

{[}15\^{}{]} D. J. Bernstein, N. Duif, T. Lange, P. Schwabe, B. Yang,
\High-speed high-security signatures'',Journal of Cryptographic
Engineering, September 2012, Volume 2, Issue 2, pp 77-89

{[}16\^{}{]} Cynthia Dwork, Andrew Goldberg, and Moni Naor. On
memory-bound functions for fighting spam. In Advances in Cryptology
\textbar{} CRYPTO 2003, volume 2729 of Lecture Notes in Computer
Science, pages 426-444. Springer, 2003.

{[}17\^{}{]} Fabien Coelho, Exponential Memory-Bound Functions for Proof
of Work Protocols, 2005

{[}18\^{}{]} Colin Percival, Stronger Key Derivation via Sequential
Memory-Hard Functions, presented at BSDCan'09, May 2009

{[}19\^{}{]} http://litecoin.org

{[}20\^{}{]}{[}https://nvlpubs.nist.gov/nistpubs/FIPS/NIST.FIPS.197.pdf{]}

{[}21\^{}{]}{[}https://cryptonote.org/cns/cns008.txt{]}

{[}22\^{}{]}{[}https://keccak.team/files/NoteOnKeccakParametersAndUsage.pdf{]}

{[}23\^{}{]}{[}https://docs.monero.study/proof-of-work/cryptonight/{]}

\end{document}
